### 2021-04-09 conclusion.tex
references on horne
more on related work

\subsubsection*{Ties with logic}
The correspondence between logic and types lays the foundation for functional programming~\cite{wadler15}. Since its inception by Girard~\cite{girard87}, linear logic has been a candidate for a foundational correspondence for concurrent programs. A~correspondence with linear $\pi$-calculus was established early on by Abramsky~\cite{abramsky94,bellinscott94}. A~correspondence between session-typed $\pi$-calculus and dual intuitionistic linear logic was developed by Caires and Pfenning~\cite[$\pi\text{DILL}$]{cairespfenning10}, and with classical linear logic by Wadler~\cite[CP]{wadler15}, both guaranteeing deadlock freedom as a result of their connection to logic. Dardha and Gay~\cite[PCP]{dardhagay18} integrate Kobayashi and Padovani's work on priorities~\cite{kobayashi06,padovani14} with CP, creating the first calculus which combines priorities and strong ties with logic. Dardha and P\'{e}rez~\cite{dardhaperez15} compare Kobayashi-style typing and CLL typing, and show that CLL corresponds to a subsystem of Kobayashi's where restriction is applied once. Balzer~\etal~\cite[$\text{SILL}_S$]{balzerpfenning17} introduce shared state, which breaks deadlock freedom. They later restore deadlock freedom using priorities~\cite[$\text{SILL}_{S+}$]{balzertoninho19}.
Carbone~\etal~\cite{CarboneMSY15,carbonelindley16} give a logical view of MPST with a generalised duality, called \emph{coherence}.

>>>>

\subsubsection*{Ties with logic}
The correspondence between logic and types lays the foundation for functional programming~\cite{wadler15}. Since its inception by Girard~\cite{girard87}, linear logic has been a candidate for a foundational correspondence for concurrent programs. A~correspondence with linear $\pi$-calculus was established early on by Abramsky~\cite{abramsky94} and Bellin and Scott~\cite{bellinscott94}. Many years later, a correspondence between the $\pi$-calculus with binary session types and linear logic was proposed: Caires and Pfenning~\cite[$\pi\text{DILL}$]{cairespfenning10} proposed a correspondence with dual intuitionistic linear logic, while Wadler~\cite[CP]{wadler14} proposed a correspondence with classical linear logic. Both works guarantee deadlock freedom as result of their connection to logic and in particular due to the fact that the cut rule only allows tree-structured processes. Dardha and Gay~\cite[PCP]{dardhagay18} integrate Kobayashi and Padovani's work on priorities~\cite{kobayashi06,padovani14} with CP, creating the first calculus which combines priorities and logic. They prove cycle-elimination, in the same lines as cut-elimination for linear logic, from which the meta-theory and deadlock freedom follow. Dardha and P\'{e}rez~\cite{dardhaperez15} compare Kobayashi-style typing and CLL typing, and show that CLL corresponds to a subsystem of Kobayashi's where restriction is applied once. Balzer~\etal~\cite[$\text{SILL}_S$]{balzerpfenning17} introduce sharing, which breaks deadlock freedom. They later restore deadlock freedom using priorities~\cite[$\text{SILL}_{S+}$]{balzertoninho19}.
Carbone~\etal~\cite{CarboneMSY15,carbonelindley16} give a logical view of MPST with a generalised duality, called \emph{coherence}.
Caires and P\'{e}rez~\cite{CairesP16} give a novel presentation of MPST in terms of binary session types and the use of a \emph{medium process} which guarantee protocol fidelity and deadlock freedom. Their binary session types are rooted in linear logic following the proofs-as-processes correspondences.
Ciobanu and Horne~\cite{CiobanuH15} give the first processes-as-formulae correspondence of MPST and \emph{the calculus of structures} by \cite{Guglielmi07}, and give a calculus where global and local session types are specified inspired by Scribble\footnote{\url{http://www.scribble.org/}}. The calculus is then used to determine whether a set of local session types can be composed safely and in a deadlock free manner.
Horne \cite{Horne20} presents a proof system for subtyping and multiparty compatibility where compatible processes are race free and deadlock free. This work also gives a processes-as-formulae correspondence--similar to the approach in~\cite{CiobanuH15}--with a non-commutative extension of linear logic. As such, the meta-theoretical results of this work are obtained in terms of cut-elimination.
